Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-07-27 doc/RMD/mlg-mcg.Rmd
remake

```{r mlg accumulation calculation}
bd         <- bruvo.dist(dat11, replen = other(dat11)$REPLEN)
thresholds <- filter_stats(dat11, distance = bd, plot = TRUE)
thresh     <- c(0, unique(thresholds$farthest$THRESHOLDS) + .Machine$double.eps)
collapsed  <- map(thresh, . %>% mlg.filter(dat11, threshold = ., distance = bd))

@@

```{r mlg accumulation noclump, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = sample(87, 366, replace = TRUE)) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg accumulation mlg, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = mll(dat11, "original")) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg accumulation uniq, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = seq(366)) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg accumulation ten, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = sample(10, 366, replace = TRUE)) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg accumulation observed, fig.width = 5, fig.height = 3}
observed <- map2_df(collapsed, thresh, compare_mlg, original = mll(dat11, "custom")) %>%
  mutate(sample_number = "observed") %>%
  mutate(source = "observed")

>>>>

```{r mlg_accumulation_calculation}
bd         <- bruvo.dist(dat11, replen = other(dat11)$REPLEN)
thresholds <- filter_stats(dat11, distance = bd, plot = TRUE)
thresh     <- c(0, unique(thresholds$farthest$THRESHOLDS) + .Machine$double.eps)
collapsed  <- map(thresh, . %>% mlg.filter(dat11, threshold = ., distance = bd))

@@

```{r mlg_accumulation_noclump, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = sample(87, 366, replace = TRUE)) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg_accumulation_mlg, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = mll(dat11, "original")) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg_accumulation_uniq, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = seq(366)) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg_accumulation_ten, fig.width = 5, fig.height = 3}
map2_df(collapsed, thresh, compare_mlg, original = sample(10, 366, replace = TRUE)) %>%
  ggplot(aes(x = threshold, y = N)) +
  geom_point(alpha = 0.1) +
  stat_smooth(se = FALSE, color = "black") +
  stat_summary(pch = 21, fun.data = my_meanse, fill = "white")
```

@@

```{r mlg_accumulation_observed, fig.width = 5, fig.height = 3}
observed <- map2_df(collapsed, thresh, compare_mlg, original = mll(dat11, "custom")) %>%
  mutate(sample_number = "observed") %>%
  mutate(source = "observed")
